---
title: "Benchmark of the CPP vs R functions for homework"
author: "Baltazar Bieniek"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

This vignette describes the benchmark for the homework 6.

## Mode function

The following R function has been used to compare the performance of cpp and R solution:

```{r}
modeR <- function(x) {
  as.numeric(names(table(x))[which.max(table(x))]) 
}
```

The benchmark for the function is as follows:
```{r}
require(microbenchmark)
x<-sample(1:100, replace=TRUE, 100000)
microbenchmark(mode(x), modeR(x))
x<-sample(1:1000, replace=TRUE, 100000)
microbenchmark(mode(x), modeR(x))
```

## Simplify2array function

To compare the performance against R, we used unlist function


The benchmark for the function is as follows:
```{r}
require(microbenchmark)
x<-replicate(1000, sample(1:100,size=10), simplify=FALSE)
microbenchmark(simplify2array(x), unlist(x))
x<-replicate(10000, sample(1:100,size=100), simplify=FALSE)
microbenchmark(simplify2array(x), unlist(x))
```


## Perms

The following R function has been used to generate all permutations of a given vector:

```{r}
permutations <- function(n){
    if(n==1){
        return(matrix(1))
    } else {
        sp <- permutations(n-1)
        p <- nrow(sp)
        A <- matrix(nrow=n*p,ncol=n)
        for(i in 1:n){
            A[(i-1)*p+1:p,] <- cbind(i,sp+(sp>=i))
        }
        return(A)
    }
}
```

The benchmark for the function is as follows:
```{r}
require(microbenchmark)
x<-replicate(5, sample(1:100,size=3), simplify=FALSE)
microbenchmark(lapply(x, bbhw6::perms), lapply(x,permutations))
x<-replicate(10, sample(1:100,size=4), simplify=FALSE)
microbenchmark(lapply(x, bbhw6::perms), lapply(x,permutations))
```

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
