---
title: "Benchmark of the CPP vs R functions for homework"
author: "Baltazar Bieniek"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

This vignette describes the benchmark for the homework 6.

## Mode function

The following R function has been used to compare the performance of cpp and R solution:

```{r}
modeR <- function(x) {
  as.numeric(names(table(x))[which.max(table(x))]) 
}
```

The benchmark for the function is as follows:
```{r}
require(microbenchmark)
x<-sample(1:100, replace=TRUE, 100000)
microbenchmark(mode(x), modeR(x))
x<-sample(1:1000, replace=TRUE, 100000)
microbenchmark(mode(x), modeR(x))
```


## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
